\documentclass[12pt]{article}
\usepackage{times}
\usepackage{amsmath}
\usepackage{a4}
\usepackage{graphicx}
\usepackage{subfigure}

%\setlength{\textwidth}{6in}
\setlength{\textheight}{9in}
\pagestyle{empty}
%\setlength{\oddsidemargin}{0.5in}
%\setlength{\evensidemargin}{-0.5in}
%\setlength{\textwidth}{in}
\begin{document}

\begin{center}
\Large
\textbf{Computational Manybody Physics}\\
\large
Suggested Projects
\date{today}
\end{center}
\begin{itemize}
\item Classical Monte Carlo
\begin{enumerate}
\item Kinetic Monte Carlo:
A. B. Bortz and M. H. Kalos and J. L. Lebowitz, "A new algorithm for Monte Carlo simulation of Ising spin systems", Journal of Computational Physics \textbf{17}, 10 (1975) 
\item Wang-Landau Algorithm: Fugao Wang and D. P. Landau, "Efficient, Multiple-Range Random Walk Algorithm to Calculate the Density of States", Phys. Rev. Lett. \textbf{86}, 2050 (2001)
\item Parallel tempering algorithm:  David J. Earl and Michael W. Deem (2005) "Parallel tempering: Theory, applications, and new perspectives", Phys. Chem. Chem. Phys., 7, 3910 (2005).
\item Multicanonical Monte Carlo:    Bernd A. Berg and Thomas Neuhaus , "Multicanonical ensemble: A new approach to simulate first-order phase transitions", Phys. Rev. Lett. \textbf{68}, 9 (1992); B. A Berg, "Introduction to multicanonical Monte Carlo", arXiv: cond-mat/9909236
%The conventional Metropolis Monte Carlo, designed for equilibrium systems, is not suitable  to simulate the real-time evolution of some processes occurring in nature; in particular, the non-equilibrium processes such as diffusion, nucleation, and so on. 
\end{enumerate}
\item Exact Diagonalization
\begin{enumerate}
\item Dynamical Correlation Functions
\item Finite Temperature Lanczos Method
\end{enumerate}
\item DMRG
\begin{enumerate}
\item Transfer-Matrix DMRG: Stefan Glocke, Andreas Kl\"{u}mper, and Jesko Sirker, "The density-matrix renormalization group applied to transfer matrices: Static and dynamical properties of one-dimensional quantum systems at finite temperature", arXiv: cond-mat/0610689, Lecture Notes in Physics, Vol. 739: Computational Many-Particle Physics (Springer, Berlin, 2008)
\item Finite Temperature DMRG
\item Time-dependent DMRG
\end{enumerate}
\item Quantum Monte Carlo
\begin{enumerate}
\item Parallel tempering SSE: R. G. Melko, "Simulations of quantum XXZ models on two-dimensional frustrated lattices", J. Phys. Condens. Matter \textbf{19}, 145203 (2007).
\item Stochastic cluster series expansion: Kim Louis and C. Gros , "Stochastic cluster series expansion for quantum spin systems", Phys. Rev. B \textbf{70}, 100410(R) (2004).
\item Hybrid Monte Carlo
%\href{http://www.mcmchandbook.net/HandbookChapter5.pdf}{MCMC Using Hamiltonian Dynamics}
\item Variational Monte Carlo
\item Auxiliary field Monte Carlo
\item Directed loop algorithm in SSE
\item Worm Algorithm
\item Determinant Monte Carlo
\item Diffusion Monte Carlo

\end{enumerate}
\end{itemize}
\end{document}
